---
title: "Viv Benchmarks"
subtitle: "Comparison of HTTP Protocol Versions, Image File Formats, and Tile Sizes"
date: "9 October 2020"
output: html_document
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Parse Data

```{r message=FALSE}
http2 = read_csv("chrome_http2.csv") %>% mutate(protocol = "http2")
http1 = read_csv("chrome_http1.csv") %>% mutate(protocol = "http1")
```

# Merge and Calculate Additional Variables

```{r warning=FALSE, message=FALSE}
data = bind_rows(http1, http2) %>%
  mutate(
    viewport = paste(height, width, sep = 'x'),
    tileTime = endTime - startTime,
    # loading time normalized to account for tile size (relative to 256x256 tile size)
    tileTimeNormalized = (endTime - startTime) / (tileSize**2 / 256**2),
    # loading time per pixel across all channels
    pixelTime = (endTime - startTime) / tileSize**2,
    # loading time per pixel normalized to account for channel count
    pixelTimeNormalized = (endTime - startTime) / (tileSize**2 * numChannels),
  )
```

# View Loading Times

A view is defined as a set of tiles needed to visualize a viewport for a specific region across all zoom levels with a set number of channels. Assuming negligible rendering times, the times shown here correspond to the aggregate wait times that a user would experience after navigating to the view and zooming across all zoom levels. 

```{r warning=FALSE, message=FALSE}
merged_data <- data %>%
  # fix channel count
  filter( numChannels==4 ) %>%
  # group by protocol, format, regionId, viewport, tileSize, iteration
  group_by( iter, protocol, format, regionId, viewport, tileSize, numChannels, zoom ) %>%
  # compute statistics per view, i.e., for a given region id and viewport size
  summarize(minStartTime=min(startTime), maxEndTime=max(endTime), tiles=n()) %>%
  mutate(
    viewTime = maxEndTime-minStartTime,
    viewport = factor(viewport, levels=c('1920x1080', '1000x1000', '300x400'))
  )

plot <-
  ggplot( merged_data ) +
  aes( y=viewTime, x=format, fill=protocol ) +
  geom_violin() +
  facet_grid(cols=vars(tileSize), rows=vars(viewport)) +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  labs(
    title="Time to Load all Tiles in View (4 channels)",
    y="View Time (ms)",
    x="Format",
    fill="Protocol"
  ) + 
  theme_minimal()
plot
```

# Sanity Checks

## Correlation between Iteration and Tile Loading Times (4 channels)

```{r warning=FALSE, message=FALSE}
plot <- 
  ggplot( data  %>% filter( numChannels==4 ) ) +
  aes( x=as.factor(iter), y=tileTime ) +
  geom_violin() +
  facet_grid(rows=vars(tileSize),cols=vars(format), scales="free") +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  labs(
    title="Time to Load Tile",
    x="Iteration",
    y="Tile Time (ms)"
  ) +
  theme_minimal()
plot
```

## Correlation between Region and Tile Loading Times: Formats

```{r warning=FALSE, message=FALSE}
plot <- 
  ggplot( data  %>% filter( numChannels==4 ) ) +
  aes( x=as.factor(regionId), y=tileTime ) +
  geom_violin() +
  facet_grid(rows=vars(tileSize),cols=vars(format), scales="free") +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  labs(
    title="Time to Load Tile",
    x="Region",
    y="Tile Time (ms)"
  ) +
  theme_minimal()
plot
```

## Correlation between Region and Tile Loading Times: Protocols

```{r warning=FALSE, message=FALSE}
plot <- 
  ggplot( data  %>% filter( numChannels==4 ) ) +
  aes( x=as.factor(regionId), y=tileTime ) +
  geom_violin() +
  facet_grid(rows=vars(tileSize),cols=vars(protocol), scales="free") +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  labs(
    title="Time to Load Tile",
    x="Region",
    y="Tile Time (ms)"
  ) +
  theme_minimal()
plot
```

## Correlation between Zoom Level and Tile Loading Times

```{r warning=FALSE, message=FALSE}
plot <- 
  ggplot( data  %>% filter( numChannels==4 ) ) +
  aes( x=as.factor(zoom), y=tileTime ) +
  geom_boxplot() +
  facet_grid(rows=vars(tileSize),cols=vars(format), scales="free") +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  labs(
    title="Time to Load Tile",
    x="Zoom Level",
    y="Tile Time (ms)"
  ) +
  theme_minimal()
plot
```

```{r warning=FALSE, message=FALSE}
plot <- 
  ggplot( data  %>% filter( numChannels==4 ) ) +
  aes( x=as.factor(zoom), y=tileTime ) +
  geom_point() +
  facet_grid(rows=vars(tileSize), cols=vars(format), scales="free") +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  labs(
    title="Time to Load Tile",
    x="Zoom Level",
    y="Tile Time (ms)"
  ) +
  theme_minimal()
plot
```


# In-Depth Comparison of HTTP Protocol Versions

## Comparison of Individual Tile Loading Times between HTTP1 and HTTP2
```{r}
merged_data <- data %>%
  filter( regionId == "Zoomed In" ) %>%
  filter( format == "zarr" ) %>%  
  filter( tileSize == 256 ) %>%    
  filter( numChannels == 4 ) %>%  
  group_by(iter,format,numChannels,tileSize,regionId,zoom,viewport,tileId) %>%
  arrange(protocol,.by_group=TRUE) %>%
  summarize(http1Time=first(tileTime), http2Time=last(tileTime))

plot <- 
  ggplot( merged_data ) +
  aes( x=http1Time, y=http2Time, color=as.factor(iter), shape=format ) +
  geom_point( alpha=0.3 ) +
  coord_fixed() +
  facet_grid(rows=vars(tileSize), cols=vars(zoom, regionId, format)) +
  scale_x_continuous(guide = guide_axis(angle = 90)) +
  theme_minimal()
plot
```

# In-Depth Comparison of Image Formats

## Comparison of Individual Tile Loading Times between OME-TIFF and Zarr
```{r}
merged_data <- data %>%
  group_by(iter,protocol,numChannels,tileSize,regionId,zoom,viewport,tileId) %>%
  arrange(format,.by_group=TRUE) %>%
  summarize(omeTiffTime=first(tileTime), zarrTime=last(tileTime))

plot <- 
  ggplot( merged_data ) +
  aes( x=omeTiffTime, y=zarrTime, color=regionId, shape=protocol ) +
  geom_point() +
  facet_grid(rows=vars(tileSize), cols=vars(regionId, protocol), scales="free") +
  scale_x_continuous(guide = guide_axis(angle = 90)) +
  theme_minimal()
plot
```